\section{Biography}
\small
Abodh Poudyal received the B.E. degree from the Department of Electrical Engineering, Pulchowk Campus, Kathmandu, Nepal, in 2016, and the M.S. degree from the Electrical Engineering and Computer Science Department, South Dakota State University, Brookings, SD, USA, in 2018. He is currently pursuing his Ph.D. in Electrical Engineering at Washington State University, Pullman, WA, USA. His research interests include power distribution modeling and optimization, resilience assessment, modeling extreme events and their impact on the power grid, and AI-based applications on the power grid.
\singlespacing

\subsection{Publications}
\small
\begin{enumerate}
    \item {\textbf{\underline{A. Poudyal}}, S. Poudel, and A. Dubey, ``Risk-Based Active Distribution System Planning for Resilience Against Extreme Weather Events", \textit{IEEE Transactions on Sustainable Energy}, vol. 14, no. 2, pp. 1178-1192, Apr. 2023.}
    \item \textbf{\underline{A. Poudyal}}, S. Poudel, and A. Dubey, ``Trade-off Analysis and Resource Optimization in Power Distribution Systems for Resilience Against Extreme Weather Events", \textit{in preparation for Advances in Applied Energy.}
    \item S. Paul, \textbf{\underline{A. Poudyal}}, S. Poudel, and A. Dubey, ``Resilience Metrics and Planning in Power Distribution Systems: Past and Future Considerations", \textit{in preparation for Renewable and Sustainable Energy Reviews.}
    \item {\textbf{\underline{A. Poudyal}}, V. Iyenger, D. G. Camaro, and A. Dubey, ``Spatiotemporal Impact Assessment of Hurricanes on Electric Power Systems", in \textit{2022 IEEE PES General Meeting}, Jul. 2022, pp. 1-5. \textcolor{red}{\textbf{(Selected in the Best Conference Papers Session)}}}
    
    \item {\textbf{\underline{A. Poudyal}}, S. Poudel, and A. Dubey, ``A Risk-Driven Probabilistic Approach to Quantify Resilience in Power Distribution Systems", in \textit{International Conference on Probabilistic Methods Applied to Power Systems (PMAPS)}, Jun. 2022, pp. 1-6.}
    
    \item \textbf{\underline{A. Poudyal}}, A. Dubey, et al., ``Impact Assessment of Hurricanes and Storm Surges in Electric Power Systems ", accepted in \textit{2023 IEEE PES General Meeting}.
    \item {\textbf{\underline{A. Poudyal}} and A. Dubey, ``Sensitivity Analysis in risk-based resilience planning of power distribution systems", submitted for review in \textit{2023 Industrial Applications Society (IAS) Annual Meeting}.}
\end{enumerate}

  
\clearpage
\subsection{Course Work}
% \usepackage{booktabs}
\begin{table}[h!]
\centering
\setlength{\tabcolsep}{4pt}
%\caption{}
\label{tab:my-table}
\begin{adjustbox}{width=1\textwidth,center=\textwidth}
\begin{tabular}{@{}l|l|l|l@{}}
\toprule
Course Number and Name                          & Semester       & Instructor                     & Grade \\ \midrule
E\_E 521 Analysis of Power Systems              & Fall 2020      & Dr. Anjan Bose                 & A    \\
CPT\_S 553 Graph Theory                         & Fall 2020      & Dr. Matthew Hudelson           & A     \\
CPT\_S 575 Data Science                         & Fall 2020      & Dr. Assefaw Gebremedhin        & A     \\
MATH 511 Advanced Linear Algebra                & Spring 2021    & Dr. Michael Tsatsomeros        & A    \\
INTERDIS 501 Research Communication             & Fall 2021      & Dr. Allison Coffin             & A    \\
MATH 564 Convex and Nonlinear Optimization      & Fall 2021      & Dr. Tom Asaki                  & A     \\
E\_E 523 Power Systems Stability                & Spring 2022    & Dr. Mani V. Venkatasubramanian & A-    \\
MATH 565 Nonsmooth Analysis and Optimization    & Spring 2022    & Dr. Tom Asaki                  & AU    \\
    E\_E 582 Power System Economics and Markets\tablefootnote{\label{note1}currently taking this semester}     & Spring 2023    & Dr. Josue Campos do Prado      &      \\
    E\_E 595 Directed study in Electrical Engineering\textsuperscript{\ref{note1}} & Spring 2023    & Dr. Anamika Dubey      &      \\
    MATH 567 Integer and Combinatorial Optimization\textsuperscript{\ref{note1}} & Spring 2023    & Dr. Bala Krishnamoorthy         & AU \\ \bottomrule
\end{tabular}
\end{adjustbox}
\end{table}
